\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}% Tweak page margins
\usepackage{graphicx} % Required for inserting images
\usepackage{float} % Positioning of figures
\usepackage{xcolor}
\usepackage{tikz-cd}
%\usepackage{tikz-cd}
\usepackage[most]{tcolorbox}
\usepackage[outputdir=../]{minted}
\usepackage{biblatex}
%\bibliography{ref}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage{forest}



\definecolor{folderbg}{RGB}{124,166,198}
\definecolor{folderborder}{RGB}{110,144,169}

\def\Size{4pt}
\tikzset{
  folder/.pic={
    \filldraw[draw=folderborder,top color=folderbg!50,bottom color=folderbg]
      (-1.05*\Size,0.2\Size+5pt) rectangle ++(.75*\Size,-0.2\Size-5pt);  
    \filldraw[draw=folderborder,top color=folderbg!50,bottom color=folderbg]
      (-1.15*\Size,-\Size) rectangle (1.15*\Size,\Size);
  }
}


\title{Molecular programming with \textit{CRN++}, a 02257 project}
\author{
    Hans Henrik Hermansen s194042\\
    Jonathan S. Højlev s194684\\
    Rani Ey. í Bø s194067}
\date{26/06 2024}

\begin{document}
\pagenumbering{gobble}

\maketitle
\section{Abstract}
This report explores our implementation of the CRN++ programming language as outlined by Vasic, Soloveichik, and Khurshid. Our primary aim was to deepen our proficiency with the F\# programming language by translating CRN++ into functional software components. We improved the grammar and the type checker, parser and more. Additionally, we made the solution to the ODE more efficiently computable, by integrating matrix operations. These optimizations made the simulations much faster, which among other things enabled us to introduce more tests. Speaking of tests, our work also included many tests that aim to verify the functionality of the code. Furthermore, we developed visualization tools to graphically depict the dynamic changes in chemical concentrations over time.\\

Through this project, we not only enhanced our technical skills in F\# but also gained insight into the cool world of chemical computation. It was cool to learn how chemistry is Turing complete and to us the functional paradigm to implement a, for us, totally novel, fully parallel, chemical programming paradigm.




\newpage

\pagenumbering{arabic}

\input{report/1.crn_interpreter}
\input{report/2.chemical_reaction}
\input{report/3.compiling}
\input{report/4.evaluation}

\newpage
\input{report/Appendix}
%\printbibliography

\end{document}
